\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-24 abstract.tex
Challenge#2
Some Comments.

With the growing practice of mechanizing language metatheories,
it has become ever more pressing that interactive theorem provers 
make it easy to write reusable, extensible code and proofs.
%
This paper presents a language design useful for extensible metatheory
mechanization in a proof assistant.
The new design achieves reuse and extensibility via a form of family
polymorphism, a seemingly object-oriented idea, that allows code and
proofs to be polymorphic to their enclosing families.
Our development addresses significant technical challenges that arise
from the underlying language of a proof assistant being simultaneously
functional, dependently typed, a logic, and an interactive tool.
%
Our results include
\begin{enumerate*}
\item a prototypical implementation of the language design as a Coq plugin,
\item a formalization of the language design as a constructive type theory with inductive types,
\item proofs of strong guarantees afforded by the type theory,
and 
\item case studies showing how the new expressiveness naturally addresses real
programming challenges in metatheory mechanization.
\end{enumerate*}

>>>>

With the growing practice of mechanizing language metatheories,
it has become ever more pressing that interactive theorem provers 
make it easy to write reusable, extensible code and proofs.
%
This paper presents a language design geared towards extensible metatheory
mechanization in a proof assistant.
The new design achieves reuse and extensibility via a form of family
polymorphism, a seemingly object-oriented idea, that allows code and
proofs to be polymorphic to their enclosing families.
Our development addresses significant technical challenges that arise
from the underlying language of a proof assistant being simultaneously
functional, dependently typed, a logic, and an interactive tool.
%
Our results include
\begin{enumerate*}
\item a prototypical implementation of the language design as a Coq plugin,
\item a formalization of the language design as a constructive type theory with inductive types,
\item proofs of strong guarantees\EDJ{We don't yet have normalization though} afforded by the type theory,
and 
\item case studies showing how the new expressiveness naturally addresses real
programming challenges in metatheory mechanization.
\end{enumerate*}

### 2022-10-24 introduction.tex
Some Comments.

\item We present the first language design that enables extensible
metatheory mechanization in a higher-order, dependent type theory with
inductive types (\cref{sec:lang-design}).
The language design reconciles the expressiveness enabled by
family polymorphism with the exactness of a proof assistant,
while retaining an idiomatic programming style.

@@

\item We capture the essence of the new language mechanism formally by extending
Martin–Löf type theory with family polymorphism and extensible inductive
types (\cref{sec:metatheory}).
We derive strong meta\-theoretical results including consistency and
canonicity.
We also formalize the translation implemented by the Coq plugin.

>>>>

\item We present the first\EDJ{Are you sure? This claim is so bold.} language design that enables extensible
metatheory mechanization in a higher-order, dependent type theory with
inductive types (\cref{sec:lang-design}).
The language design reconciles the expressiveness enabled by
family polymorphism with the exactness of a proof assistant,
while retaining an idiomatic programming style.

@@

\item We capture the essence of the new language mechanism formally by extending
Martin–Löf type theory with family polymorphism and extensible inductive
types (\cref{sec:metatheory}).
We derive strong meta\-theoretical\EDJ{I will suggest use ``foundational'' instead. Sterling at some places say canonicity is the most basic meta-theoretical property.} results including consistency and
canonicity.
We also formalize the translation implemented by the Coq plugin.
